Dynamics of the Lower Solar Atmosphere

### 2024-08-14 main_thesis_file.tex
Updates from Overleaf

% use "plain" for committee to read, or for printing single-spaced in general
\documentclass[plain]{hvdthesis}

@@

	%% Title page
\makecover
	%% Copyright
%\copyright
	%% Abstract
\input{abstract.tex}
%\input{abstract_short.tex}
	%% Table of Contents
{\singlespace
\tableofcontents
}
\newpage
\clearpage

@@

\thispagestyle{plain}
\addcontentsline{toc}{chapter}{List of Abbreviations}
\chaptermark{List of Abbreviations}
\vskip 0.5cm
{\centerline {\Large \bf List of Abbreviations}}
\vskip 0.5cm
\normalsize

@@

\newpage
	%% Acknowledgments
%\input{acknowledge.tex}
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Acknowledgments}
\chaptermark{Acknowledgments}

@@

%\hfill -- RCH
%\newpage

\clearpage
%	%% Dedication
%\input{dedication.tex}
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Dedication}

\vspace*{\fill}
{\centerline {\em Your thoughtful dedication goes here.}}
%\vskip 1.5cm
%{\centerline {\em }}
\vspace*{\fill}

@@

\chapter[Introduction]{Introduction}\label{c:intro}
\input{./introduction/intro}
\clearpage
%
\chapter{Existing Solar Observations and Techniques: A bridge towards Solar Ultraviolet Imaging Telescope}\label{c:chap2}
\chaptermark{Solar Observatories and Analysis Techniques}
\input{./chapter2/ms.tex}
\clearpage
%
\chapter{Intital preparatory analysis for SUIT}\label{c:chap3}
\chaptermark{SUIT preparatory analysis}
\begin{quote}
{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{authors,
{\em journal reference info}}
\end{quote}
\input{./chapter3/ms.tex}
\clearpage
%
\chapter{Forward modelling SUIT observations}\label{c:chap4}
\chaptermark{SUIT forward model}
\begin{quote}
{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{authors,
{\em journal reference info}}
\end{quote}
\input{./chapter4/ms.tex}
%
%\chapter{Stellar calibration of SUIT}\label{c:chap5}
%\chaptermark{SUIT stellar calibration}
%\begin{quote}
%{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
%{authors,
%{\em journal reference info}}
%\end{quote}
%\input{./chapter5/ms.tex}
%
\chapter{Effects of Solar flares on the local plasma environment from Mg II observations}\label{c:chap5}
\chaptermark{Solar flares Mg II}
\begin{quote}
{ ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{{\em The Evolution of the Ratio of \ion{Mg}{2} Intensities During Solar Flares, Roy, S., \& Tripathi, D. 2024, ApJ, 964, 106, doi:\href{https://iopscience.iop.org/article/10.3847/1538-4357/ad2a46}{10.3847/1538-4357/ad2a46}}.}
\end{quote}
\input{./chapter5/ms.tex}
\clearpage
%
\chapter{Estimating thermal energy of two Solar Flares}\label{c:chap6}
\chaptermark{Solar flare energy}
\begin{quote}
{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{authors,
{\em journal reference info}}
\end{quote}
\input{./chapter6/ms.tex}
\clearpage
%
\chapter{First flares observed from {\suit}}\label{c:chap7}
\chaptermark{Solar flare energy}
\begin{quote}
{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{authors,
{\em journal reference info}}
\end{quote}
\input{./chapter7/ms.tex}
\clearpage
%

% I changed  thebibliography in hvdthesis.cls, so that it generates
% a ToC entry, and is headed References instead of Bibliography. -HJC
\singlespace
\bibliographystyle{apj}
\bibliography{your_bib_file}

>>>>

% use "plain" for committee to read, or for printing single-spaced in general
\documentclass[keepsake]{hvdthesis}

@@

	%% Title page
\makecover
	%% Copyright
%\copyright

\thispagestyle{plain}
{\centerline {\em "The first principle is that you must not fool yourself, }}
{\centerline {\em and you are the easiest person to fool."}}
{\rightline {\em {--} Richard P. Feynman}}

\newpage
	%% Abstract
\input{abstract.tex}
%\input{abstract_short.tex}
	%% Table of Contents
{\singlespace
\tableofcontents
}
\newpage
\clearpage

@@

\newpage
\clearpage

\thispagestyle{plain}
%\addcontentsline{toc}{chapter}{List of Publications}
\chaptermark{List of Publications}
\vskip 0.5cm
{\centerline {\Large \bf List of Publications}}
\vskip 0.5cm
\normalsize

\input{pub.tex}

\newpage
\clearpage

\thispagestyle{plain}
\addcontentsline{toc}{chapter}{List of Abbreviations}
%\chaptermark{List of Abbreviations}
\vskip 0.5cm
{\centerline {\Large \bf List of Abbreviations}}
\vskip 0.5cm
\normalsize

@@

\newpage
\clearpage
	%% Acknowledgments
%\input{acknowledge.tex}
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Acknowledgments}
\chaptermark{Acknowledgments}

@@

%\hfill -- RCH

\newpage
\clearpage
%	%% Dedication
%\input{dedication.tex}
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Dedication}

\vspace*{\fill}
{\centerline {\em Dedicated to everyone who pushed me one step at a time,}} 
{\centerline {\em every time I was about to give up!}}
{\centerline {\em And to my younger self, who was brave enogh to embark on this journey...}}
%\vskip 1.5cm
%{\centerline {\em }}
\vspace*{\fill}

@@

\chapter[Introduction]{Introduction}\label{c:intro}
\input{./introduction/intro}
\clearpage
%
\chapter{Existing Solar Observations and Techniques: A bridge towards Solar Ultraviolet Imaging Telescope}\label{c:chap2}
\chaptermark{Solar Observatories and Analysis Techniques}
\input{./chapter2/ms.tex}
\clearpage
%
\chapter{Intital preparatory analysis for SUIT}\label{c:chap3}
\chaptermark{SUIT preparatory analysis}
\input{./chapter3/ms.tex}
\clearpage
%
\chapter{Forward modelling SUIT observations}\label{c:chap4}
\chaptermark{SUIT forward model}
\begin{quote}
{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{authors,
{\em journal reference info}}
\end{quote}
\input{./chapter4/ms.tex}

%
\chapter{Effects of Solar flares on the local plasma environment from Mg II observations}\label{c:chap5}
\chaptermark{Solar flares Mg II}
\begin{quote}
{ ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{{\em The Evolution of the Ratio of \ion{Mg}{2} Intensities During Solar Flares, Roy, S., \& Tripathi, D. 2024, ApJ, 964, 106, doi:\href{https://iopscience.iop.org/article/10.3847/1538-4357/ad2a46}{10.3847/1538-4357/ad2a46}}.}
\end{quote}
\input{./chapter5/ms.tex}
\clearpage
%
\chapter{Estimating thermal energy of two Solar Flares}\label{c:chap6}
\chaptermark{Solar flare energy}
\begin{quote}
{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{authors,
{\em journal reference info}}
\end{quote}
\input{./chapter6/ms.tex}
\clearpage
%
\chapter{First flares observed by {\suit}}\label{c:chap7}
\chaptermark{First Flares observed with SUIT}
\begin{quote}
{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{authors,
{\em journal reference info}}
\end{quote}
\input{./chapter7/ms.tex}
\clearpage
%

\chapter{Echoes of the Solar Inferno: Summary and Future Prospects}\label{c:chap8}
\chaptermark{Outlook}
\input{./chapter8/ms.tex}
\clearpage

% I changed  thebibliography in hvdthesis.cls, so that it generates
% a ToC entry, and is headed References instead of Bibliography. -SR
\singlespace
%\bibliographystyle{aasjournal}
\bibliography{your_bib_file}
